Meta-analysis of fungicide application timing experiments for powdery mildew

### 2020-05-22 01_Meta-analysis_experiments.Rmd
as per repository issue #20 column heading and contents made more clear and removed trial_ref

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, leaflet, htmltools)
source("R/import_data.R")
```

@@

kable(
   PM.dat %>%
      group_by(trial_ref, ) %>%
      summarise(
         year = unique(year),
         location = unique(location),
         mean_treat_replicates = mean(replicates),
         planting_date = unique(planting_date),
         first_sign_disease = unique(first_sign_disease),
         treatments = length(n_treatment)
      ) %>%
      arrange(year),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```

>>>>

```{r MEsummary_Libraries, message=FALSE, echo=FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, kableExtra, leaflet, htmltools,schoolmath)
source("R/import_data.R")
```

@@

kable(
   PM.dat %>%
      group_by(trial_ref, ) %>%
      summarise(
         year = unique(year),
         location = unique(location),
         replicates_per_treatment = if(is.whole(mean(replicates))){
            as.character(mean(replicates))}else{
               as.character(paste(min(replicates),"-",max(replicates)))},
         planting_date = unique(planting_date),
         first_sign_disease = unique(first_sign_disease),
         treatments = length(n_treatment)
      ) %>%
      arrange(year)%>%
      select(-trial_ref),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")

```
